---
title: "My First Report"
author: "Humaira"
format:
  html:
    embed-resources: true
---

## Welcome to your practice report

This is a **Quarto** document. It mixes ordinary writing with live code, so your
report and your analysis always stay in sync. When you click **Render**, Quarto
runs the code below and builds a finished HTML page.

Try it now: change `author: "Your Name"` in the header above to your own name,
then click **Render**.

## A first look at the data

The code chunk below reads a small practice dataset from the `data/` folder and
shows the first few rows.

```{r}
patients <- read.csv("data/patients.csv")
head(patients)
```

## A first chart

```{r}
hist(patients$age,
     main = "Age distribution of practice patients",
     xlab = "Age (years)",
     col  = "steelblue")
```

## Your turn

The chart is a histogram. Very cool. 

When you are happy with the result, **commit and sync** your work (the Week 2
course page walks you through this), then submit your repository link on Canvas.

## My notes 

The **easiest** thing was opening files and loading them onto the codespace 
It was **hard** to get the html thing to open in a nice clean format. I did open it once and it looked different from what the instructor was showing us.
I don't have any questions as of now. 


```{r}
summary (patients)
```
